\ttitle

### 2013-05-23 Chapters/Chapter2/svm.tex
Add introduction Chapter 2
Finish SVM summary

% !TEX root = ../../main.tex
\section{Change-detection by Support Vector Machines}

@@

\subsection{One-class Support Vector Machine}
The proposed method of Camci \cite{camci2010change} uses a one-class support vector machine to segment time series data.
One-class SVMs are used to describe the current data under consideration, by assuming all data points are from the same class \cite{tax2001one}.
The class is described by a spherical boundary around the data with center $c$ and radius $r$, such that the volume is minimized.
Following the definition of Camci \cite{camci2010change}, the class description is obtained by minimizing $r^2$:
\begin{equation}
  \mathrm{Min}\ r^2
\end{equation}
\begin{equation}
  \mathrm{Subject\ to} : \|\mathbf{x}_i - \mathbf{c}\|^2 \le r^2\ \forall i,\ \mathbf{x}_i : i \mathrm{th\ data\ point}
\end{equation}

>>>>

% !TEX root = ../../main.tex
\section{Change-detection by Support Vector Machines}\label{svm}

@@

\subsection{One-class Support Vector Machine}

*** Replace with / add information from summary in \ref{svm-explained}. ***

The proposed method of Camci \cite{camci2010change} uses a one-class support vector machine to segment time series data.
One-class SVMs are used to describe the current data under consideration, by assuming all data points are from the same class \cite{tax2001one}.
The class is described by a spherical boundary around the data with center $c$ and radius $r$, such that the volume is minimized.
Following the definition of Camci \cite{camci2010change}, the class description is obtained by minimizing $r^2$:
\begin{equation}
  \mathrm{Min}\ r^2
\end{equation}
\begin{equation}
  \mathrm{Subject\ to} : \|\mathbf{x}_i - \mathbf{c}\|^2 \le r^2\ \forall i,\ \mathbf{x}_i : i \mathrm{th\ data\ point}
\end{equation}
